Query Optimization for Dynamic Imputation

### 2017-05-09 paper/experiments.tex
reworded caption to make clear that planning times shown don't gave optimization, just referenced in text
paper: remove implementation subsection of experiments

\subsection{Implementation}
To evaluate the performance of our approach, we implemented a prototype system in Java, following a traditional iterator model.
Our database handles a subset of standard SQL, including filters, joins, projection, grouping and aggregation.
For simplicity, \ProjectName{} only handles tables containing integer data.

@@

\subsubsection{Planning times}
\begin{table}
\centering
\input{tables/planning_summary_exact_pareto.tex}
\caption{Planning times are sub-second for up to 4 joins. For 5+  joins planning times rise. Many practical queries
can be formulated with a smaller number of joins, but to support more complex queries \ProjectName{} provides an
optimization that maintains approximate Pareto sets for queries with many joins. This reduces planning time
for queries with 7 joins by approximately 45\%, on average.}
\label{table:planning-times}
\end{table}

>>>>

@@

\subsubsection{Planning times}
\begin{table}
\centering
\input{tables/planning_summary_exact_pareto.tex}
\caption{Planning times are sub-second for up to 4 joins. For 5+  joins planning times rise. Many practical queries
can be formulated with a smaller number of joins, but to support more complex queries \ProjectName{} provides an
optimization that maintains approximate Pareto sets for queries with many joins. This reduces the 29 second
planning time shown for 7 joins by approximately 45\%, on average.}
\label{table:planning-times}
\end{table}
